\section{Related Work}

\subsection{Demand Forecasting and Inventory Implications}

Demand forecasting research studies how predictive models can estimate future demand across products, stores, regions, and time periods. Forecast-accuracy metrics are well studied, including known limitations of comparing series using error measures alone \citep{hyndman2006accuracy}. Retail demand competitions such as M5 have further emphasized large-scale empirical forecasting under hierarchical product-store structure \citep{makridakis2022m5}. A closely related stream connects forecast quality to downstream inventory and service outcomes through inventory-control and production-planning models \citep{silver1998inventory,axsater2015inventory}. This paper builds on that operational motivation but focuses on an intermediate layer that is often left implicit: the conversion of candidate forecasts into planning signals that must be executed under finite adjustment capacity.

\subsection{Forecast Combination and Model Selection}

Forecast-combination and model-selection methods provide mechanisms for choosing among or aggregating candidate forecasts. Classic forecast-combination work shows why averaging or weighting forecasts can be useful when no single candidate is uniformly best \citep{bates1969combination}. Modern empirical forecasting pipelines also commonly include tree-based learners such as LightGBM, XGBoost, and random forests as scalable nonlinear candidates \citep{ke2017lightgbm,chen2016xgboost,breiman2001random}. Standard selection criteria often prioritize forecast error on validation data. The present paper differs by evaluating deployable planning utility rather than forecast error alone. A forecast combination can be attractive not only because it improves accuracy, but because it reduces abrupt plan changes, spreads model risk, or avoids unnecessary switching.

\subsection{Cost-Sensitive and Multi-Objective Decision Making}

Cost-sensitive and multi-objective decision methods are related because demand planning rarely has a single objective. Inventory cost, service level, volatility, and execution burden can move in different directions. Rolling-horizon decision models provide a natural connection between forecast updates and finite-horizon planning decisions \citep{sethi1991rolling}. The contribution here is not a generic multi-objective optimizer. It is a structured operational planning evaluation framework in which forecast-driven plans are compared against execution-capacity constraints and normalized relative to an accuracy-first baseline.

\subsection{Supply-Chain Execution Risk and Planning Stability}

Supply-chain execution risk, planning nervousness, and plan volatility are central to the gap studied in this paper. Early industrial-dynamics work emphasized that operational systems can amplify instability when information and material flows respond with delays or constraints \citep{forrester1961industrial}. Advanced planning systems similarly separate planning, coordination, and execution layers in supply-chain software and governance \citep{stadtler2015advanced}. Downstream operations may be unable to absorb large changes in inventory targets, replenishment quantities, transportation commitments, or staffing plans. This paper connects forecast-driven model selection to measurable execution feasibility by using supply-chain execution evidence to define scenario weights and by evaluating planning volatility and execution violations directly.
