\section{Experimental Setup}

\subsection{Datasets}

The empirical design assigns distinct roles to the available public datasets. The goal is not to build a single forecasting leaderboard, but to test whether the accuracy-feasibility tradeoff appears across complementary operational settings.

\paragraph{DataCo (Execution Risk Calibration).} DataCo contains supply-chain order fulfillment records from a multi-product supplier. The dataset is used as an execution-risk anchor, not as a demand-forecasting benchmark. Specifically, the analysis extracts late-delivery rates (fraction of orders delayed beyond promised date) across operational contexts (product type, shipping method, geographical region). Summary statistics:
\begin{itemize}
    \item Global late-delivery rate: 54.8\%
    \item Context-level percentiles: 30th=53.5\%, 50th=55.2\%, 75th=58.1\%, 95th=90.1\%
\end{itemize}
These empirical rates inform execution-risk sensitivity scenarios applied to downstream planning evaluations.

\paragraph{Favorita (Main Proof-of-Concept).} Favorita is a public grocery sales dataset from Corporacion Favorita (Ecuador) covering January 2013--August 2017. The pipeline treats Favorita as a daily store-family demand-planning panel with product promotion, holiday, oil-price, transaction, and store-context signals. The analysis dataset structure:
\begin{itemize}
    \item \textbf{Planning units}: 54 stores $\times$ 33 product families = 1,782 store-family series
    \item \textbf{Temporal coverage}: 2013-01-01 to 2017-08-15 (4 years, 8 months)
    \item \textbf{Train / Validation / Test split}: chronological daily split with a validation horizon and test horizon of 28 days each.
        \begin{itemize}
            \item Train: 2013-01-01 to 2017-06-20 (4 years 5.5 months)
            \item Validation: 2017-06-21 to 2017-07-18 (28 days)
            \item Test: 2017-07-19 to 2017-08-15 (28 days)
        \end{itemize}
    \item \textbf{Evaluation scales}: Quick mode (100 series sampled), Medium mode (500 series), Full mode (1000 series)
\end{itemize}

\paragraph{M5 (Hierarchical Robustness).} M5 is a public retail demand dataset from Walmart covering 2011-2016 at daily granularity. It contains 3,049 items across 10 stores and supports hierarchy-aware planning views such as item-store, department-store, and category-store. The pipeline samples item-store series for quick and medium robustness runs. Dataset structure:
\begin{itemize}
    \item \textbf{Planning units}: sampled item-store series, with aggregated department-store and category-store robustness views
    \item \textbf{Temporal coverage}: 2011-01-29 to 2016-06-30 (5 years, 5 months)
    \item \textbf{Evaluation scale}: quick-mode robustness outputs have been generated; medium and full M5 modes remain optional extensions
    \item \textbf{Intermittency}: item-store demand can be sparse, so the robustness pass includes explicit intermittency-bucket summaries
\end{itemize}

\paragraph{Walmart (Business-Context Robustness).} The Walmart Recruiting Store Sales Forecasting dataset is used as a narrow robustness check, not as a new forecasting leaderboard. The analysis treats store-department-week as the planning grain and compares history-only forecasts against forecasts that also use business-context signals such as holidays, markdowns, fuel price, CPI, unemployment, store type, store size, and temperature. The purpose is to test whether weekly business context and cadence constraints alter deployable strategy rankings.

\paragraph{Rossmann (Future Extension).} Rossmann drug-store sales remain reserved for future analysis and are not used to support claims in the current draft.

\subsection{Forecasting Models}

The analysis includes transparent baselines and machine-learning candidates to test strategy behavior across forecast accuracy levels.

\subsubsection{Favorita Candidate Forecasts}

\begin{itemize}
    \item \textbf{Naive Last-Value}: $\hat{y}_{i,t} = y_{i,t-1}$ (lag-1 demand)
    \item \textbf{Seasonal Naive}: $\hat{y}_{i,t} = y_{i,t-7}$ (lag-7 daily seasonal baseline)
    \item \textbf{Moving Average}: $\hat{y}_{i,t} = \text{mean}(y_{i,t-28:t-1})$ (28-day rolling average)
    \item \textbf{Exponential Smoothing}: Holt-Winters method with $\alpha=0.3$ (adaptive smoothing with trend/seasonality)
    \item \textbf{LightGBM}: Gradient boosting with lag features (lags 1, 7, 28) + rolling statistics (mean, std)
    \item \textbf{XGBoost}: Gradient boosting with same feature set as LightGBM
\end{itemize}

Transparent baselines are always computed. Machine-learning models (LightGBM, XGBoost) are included when dependency libraries are available; in constrained environments, baseline-only evaluation remains valid.

\subsubsection{M5 Candidate Forecasts}

M5 evaluation uses transparent baselines (naive, seasonal naive, moving average, exponential smoothing) to ensure computational feasibility across all hierarchy levels and intermittency stress tests. The baseline-only design reflects a practical constraint: ML models on sparse hierarchical data require careful feature engineering that is deferred to future work.

\subsubsection{Walmart Candidate Forecasts}

Walmart evaluation uses weekly transparent baselines and a lightweight global sklearn model. Two feature sets are compared. The history-only set uses weekly lags, rolling means, rolling standard deviations, exponential smoothing, zero-demand rate, and calendar features. The history-plus-context set adds markdowns, holiday flags, fuel price, CPI, unemployment, store type, store size, and temperature. The context-aware setting tests whether business-context signals change forecast-to-plan feasibility; it is not designed as a Kaggle leaderboard forecasting model.

\subsubsection{Feature Engineering}

For ML candidates:
\begin{itemize}
    \item \textbf{Lag features}: Demand at lags 1, 7, and 28, capturing recent, weekly-cycle, and monthly-window demand patterns in the daily panel
    \item \textbf{Rolling statistics}: Mean and standard deviation of lagged demands
    \item \textbf{Known-in-advance context signals} (Favorita and Walmart): Promotion or markdown flags, holiday indicators, and store or product context where available at planning time
    \item \textbf{Lagged or exogenous context signals}: Oil-price, transaction, fuel-price, CPI, and unemployment features are handled as context variables and interpreted cautiously because they may differ in real-time availability across operational settings
    \item \textbf{Train-time only}: Features are computed from historical information available before the prediction timestamp; test outcomes are not used by deployable selectors
\end{itemize}

\subsection{Decision Strategies}

The analysis compares accuracy-first, stability-first, ensemble-based, smoothing-based, feasibility-aware adaptive, and Oracle diagnostic strategies. The baseline comparison includes BestAccuracy or Global Best, Family Best, Feasibility-Aware, Stability-Aware, Simple Ensemble, Best Inventory Cost, Best Stability, and Oracle. The improved method comparison adds feasibility-aware smoothed planning and feasibility-aware ensemble strategies. Fixed-alpha smoothing, scenario-based alpha smoothing, and utility-CV alpha smoothing are evaluated as interpretable gradual-adaptation policies. Feasibility-aware ensembles include inverse-accuracy weighting, inverse-operational-loss weighting, and a constrained validation-grid ensemble with nonnegative weights that sum to one.

\subsection{Evaluation Metrics}

The evaluation reports WAPE, inventory cost, planning volatility, execution penalty, execution violation rate, model-switching burden, normalized total loss, gap to the Realized-Inventory Oracle DP, and gap to the Realized Demand Oracle. The benchmark ladder also includes a Full-Outcome Oracle DP where available; this non-deployable diagnostic uses realized test forecast error and realized inventory outcome over the same candidate forecasts. WAPE is reported as a diagnostic forecast metric and is not part of the default operational planning objective. Normalized planning loss is reported relative to the accuracy-first BestAccuracy or Global Best baseline within the same run mode and split. Raw metrics remain visible in the result tables so that normalized rankings do not hide the underlying tradeoffs.

\subsection{Planning Parameters}

All analyses use consistent planning parameter values across datasets and run modes. Table~\ref{tab:planning-parameters} summarizes the configuration.

\begin{table}[htbp]
\centering
\caption{Planning and Execution Parameters}
\label{tab:planning-parameters}
\begin{tabular}{ll|ll}
\toprule
\textbf{Parameter} & \textbf{Value} & \textbf{Parameter} & \textbf{Value} \\
\midrule
\multicolumn{4}{c}{\textbf{Inventory Parameters}} \\
\midrule
Safety stock method & Rolling 28-day std & Holding cost per unit & \$1.00 \\
Safety stock multiplier & 0.5 & Shortage cost per unit & \$5.00 \\
\multicolumn{4}{c}{\textbf{Planning Objective Weights}} \\
\midrule
$\alpha_{\text{forecast}}$ (WAPE weight) & 0.0 & $\lambda_{\text{inventory}}$ & 1.0 \\
$\lambda_{\text{volatility}}$ (plan change) & 0.10 & $\lambda_{\text{execution}}$ & 0.10 \\
$\lambda_{\text{switch}}$ (model change) & 0.05 & & \\
\multicolumn{4}{c}{\textbf{Execution Capacity}} \\
\midrule
Max plan-change rate $c_{\max}$ & 20\% & Execution capacity formula & $C_{i,t} = c_{\max} \cdot |x_{i,t-1}|$ \\
\multicolumn{4}{c}{\textbf{DP Selector Configuration}} \\
\midrule
Budgeted DP max switches & $K=2$ & Fallback policy & Incumbent-stays \\
DP planning horizon & Full test period & Switch penalty (greedy) & 0.02 per switch \\
\multicolumn{4}{c}{\textbf{Normalization Reference}} \\
\midrule
Reference strategy & Global Best / BestAccuracy & Reference group & Per dataset, run-mode, split \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Execution Capacity Scenarios}

Execution capacity scenarios evaluate how planning strategies behave when downstream operations can absorb only limited period-to-period plan changes. In the Favorita and M5 analyses, execution penalties increase when the absolute planning signal change exceeds a scenario-specific execution capacity.

\subsubsection{DataCo-to-Scenario Mapping}

DataCo-derived late-delivery-risk percentiles are mapped into execution-risk sensitivity scenarios using an additive clipped mapping:
\begin{equation}
\lambda_{\text{execution}}^{\text{scenario}} =
\mathrm{clip}\left(
    \lambda_{\text{base}}
    + \rho \cdot r_{\text{late}}^{\text{scenario}},
    \lambda_{\min},
    \lambda_{\max}
\right),
\end{equation}
where $r_{\text{late}}^{\text{scenario}}$ is the DataCo late-delivery-rate anchor and $\rho$ is a configurable risk-sensitivity coefficient.

This mapping is configurable and intended as a data-informed sensitivity design, not an exact economic calibration. The generated scenario table records the formula, late-delivery anchor, resulting $\lambda_{\text{execution}}$, data source, and fallback flag. The currently generated scenario values are:
\begin{itemize}
    \item \textbf{Baseline}: $\lambda_{\text{execution}} = 0.050$
    \item \textbf{DataCo low}: $\lambda_{\text{execution}} = 0.318$
    \item \textbf{DataCo median}: $\lambda_{\text{execution}} = 0.326$
    \item \textbf{DataCo high}: $\lambda_{\text{execution}} = 0.341$
    \item \textbf{DataCo severe}: $\lambda_{\text{execution}} = 0.500$
\end{itemize}

These scenarios should be interpreted as data-informed sensitivity weights, not as exact economic cost calibrations for Favorita or M5. When DataCo anchors are unavailable, the pipeline records fallback usage and applies configured default scenario values.

Because public demand-planning datasets do not observe internal execution-capacity limits, DataCo is used as an external execution-risk anchor. Late-delivery behavior is not identical to inventory execution violation, but both represent downstream operational inability to absorb or fulfill planning commitments. The analysis therefore transfers the empirical heterogeneity of execution risk, not exact dollar costs.

\subsection{Data Leakage Prevention}

All selectors explicitly prevent test-period outcomes from influencing model selection decisions:

\begin{itemize}
    \item \textbf{Deployable selectors} (Greedy, DP, Budgeted-DP): Use validation-calibrated expected losses and forecast-implied planning signals. Test-period actual outcomes are never accessed.

    \item \textbf{Oracle selectors} (Realized-Inventory Oracle, Full-Outcome Oracle, Realized-Demand Oracle): Explicitly marked non-deployable. Used only as diagnostic upper bounds. Test outcomes are accessed only after selection to measure gap to unrealistic oracles.

    \item \textbf{Time-split validation}: Training features and rolling statistics computed on train-only and validation-only data; test-period statistics computed only on test actuals after deployment.
\end{itemize}

The \texttt{require\_no\_future\_outcomes()} validation function is applied at selector entry points to detect and reject any test-outcome contamination.

\subsection{M5 Robustness Design}

The M5 robustness analysis tests whether the Favorita accuracy-feasibility tradeoff persists under different operational characteristics:

\begin{itemize}
    \item \textbf{Scale}: quick-mode item-store robustness with additional aggregated planning grains
    \item \textbf{Hierarchy sensitivity}: Evaluation at item-store, department-store, and category-store grains to test whether aggregation affects strategy ranking
    \item \textbf{Intermittent demand}: Stress test on sparse-demand buckets, where conventional forecasting accuracy metrics may be unstable
    \item \textbf{Temporal granularity}: Daily M5 data compared with the daily Favorita planning panel
    \item \textbf{Execution scenario robustness}: DataCo-informed scenarios applied identically to validate cross-dataset generalization
\end{itemize}

The same strategy families, selector algorithms, and normalized planning-loss formulation are reused without modification to ensure comparability.

\subsection{Walmart Business-Context Robustness Design}

The Walmart module evaluates whether business-context features and weekly planning cadence alter deployable strategy rankings. It is intentionally narrower than the Favorita and M5 analyses. The quick mode samples eligible store-department series with sufficient history and nonzero demand, medium mode increases the sample size when computationally feasible, and full mode is disabled by default.

The Walmart robustness pass includes three components:
\begin{itemize}
    \item \textbf{Context-aware versus context-free comparison}: History-only candidate forecasts are compared against history-plus-context candidate forecasts using the same deployable selectors and oracle diagnostics.
    \item \textbf{Holiday and markdown stress windows}: Normal weeks, holiday weeks, markdown-heavy weeks, and holiday-or-markdown weeks are summarized separately to test whether high-context periods change the feasibility tradeoff.
    \item \textbf{Weekly cadence constraints}: Budgeted DP uses a quarterly switch budget, a short holiday freeze window, and a maximum weekly plan-change rate. Fallback rows, if any, are reported explicitly using fallback metadata.
\end{itemize}

Walmart results are reported as business-context robustness evidence. Final interpretation will be written after reviewing the generated robustness tables and figures.

\subsection{Switch-Budget Sensitivity}

The hard switch budget $K$ is configurable and can be swept using the switch-budget sensitivity runner. This analysis reruns Budgeted DP under multiple values of $K$ while keeping the remaining planning objective fixed. The purpose is to test whether the allowed number of model switches controls the accuracy-feasibility tradeoff smoothly, not to choose $K$ after seeing test outcomes.

\subsection{Validation and Cross-Validation Design}

\subsubsection{Blocked Validation}

For smoothing-based and ensemble-reweighting strategies, hyperparameters (e.g., smoothing $\alpha$ or ensemble weights) are selected via blocked validation:
\begin{itemize}
    \item Validation period is divided into K non-overlapping folds
    \item Each fold is used as a pseudo-test period; hyperparameter loss is averaged across folds
    \item Selected hyperparameter applied to actual test period
\end{itemize}

This avoids single-point validation bias while respecting temporal ordering.

\subsubsection{Normalization Scope}

Normalized planning loss is computed within groups defined by:
\begin{itemize}
    \item Dataset, such as Favorita or M5
    \item Run mode, such as quick, medium, or full where applicable
    \item Split, such as validation or test
    \item Scenario, such as baseline or DataCo-informed execution-risk scenario
\end{itemize}

This ensures that normalizations do not mix different operational contexts, and that val-set normalization does not contaminate test-set comparison.

\subsection{Policy and Context Drift Scenarios}

Policy and context drift scenarios are reserved for subsequent robustness analysis. Candidate extensions include changes in service-level targets, shortage costs, lead times, execution capacity, and business-context covariates (seasonality changes, new product introductions, etc.).
