\section{Introduction}

\subsection{The Planning-Execution Gap}
\label{sec:gap}

Demand planning is an operational decision problem, not only a forecasting problem: forecast-driven decisions influence inventory targets, replenishment orders, supplier coordination, warehouse labor, transportation commitments, and planning-system governance. Recent advances in AI-enabled forecasting and time-series foundation models have made more accurate predictions available (Walter et al. 2025; Culot et al. 2024; Petropoulos et al. 2022; Makridakis et al. 2022), but prediction accuracy alone does not guarantee implementation success, because operations execute planning signals, not forecast error metrics. A planner cannot execute WAPE or RMSE; the organization executes an inventory target, a staffing plan, or a replenishment quantity. When forecast-driven plans change faster than supplier lead times, labor cycles, or system change windows can absorb, the forecast and execution layers become misaligned, creating a planning-execution gap in which the operation cannot execute the plan despite its accuracy.

The gap manifests in four operational symptoms:
\begin{enumerate}
\item \textbf{Execution violations}: Plans change faster than downstream systems can absorb (e.g., warehouse rescheduling, supplier coordination, system updates)
\item \textbf{Governance burden}: Each model change requires validation, coordination, and monitoring cycles, delaying adoption
\item \textbf{Supplier disruption}: Frequent plan changes force suppliers to expedite orders or renegotiate, increasing costs
\item \textbf{Operational gridlock}: Operations teams spend effort coordinating plan changes rather than executing the plan
\end{enumerate}

These symptoms are invisible in accuracy metrics but visible in execution logs, planner workload, and supplier relationships. The operational reality is that forecast accuracy and plan executability are distinct objectives.

\subsection{From Forecasting Optimization to Feasibility-Constrained Selection}

Forecasting research traditionally optimizes for accuracy, including lower WAPE, lower MAE, and better leaderboard scores. This is valuable, but a more accurate forecast that creates execution gridlock is operationally worse than a slightly less accurate forecast that executes smoothly.

The solution is to shift the evaluation target from \textit{forecast generation} to \textit{forecast-to-plan selection}: ask which planning strategy minimizes operational cost under execution constraints, not only which model minimizes WAPE. This paper operationalizes that shift as a model-agnostic forecast-to-plan feasibility layer: it converts each candidate forecast into an executable planning signal, scores its operational consequence on four metrics (inventory exposure, plan stability, execution violations, governance burden), ranks strategies by feasibility-adjusted utility rather than accuracy alone, and tests ranking stability across execution-risk scenarios and planning contexts.

\subsection{Empirical Evidence and Scope}

The empirical design uses one execution-risk anchor and three demand-planning datasets. \textbf{DataCo} anchors execution-risk scenarios from observed late-delivery heterogeneity; it is not treated as a demand-planning or inventory-control dataset. \textbf{Favorita} (main proof of concept) is daily retail demand from 54 stores and 33 product families (1,782 planning units) over 4+ years, testing whether the accuracy-feasibility tradeoff appears in richly-contexted, fine-grained planning. \textbf{M5} (hierarchy and intermittency robustness) is daily retail demand from 3,049 items across 10 stores with item-store, department-store, and category-store aggregation, testing whether strategy preferences change with granularity and demand sparsity. \textbf{Walmart} is secondary evidence only: a weekly store-department panel with markdown, holiday, and macro signals, used to check whether the same decision layer remains informative under a different cadence and business context. Across 123 paper-facing scenario and robustness evaluation groups, 91.1\% show that the WAPE-best strategy differs from the operational-loss-optimal strategy, indicating a structural result rather than a data artifact.

\subsection{Objectives}

This paper pursues five objectives, each also a research contribution:
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parsep}{0pt}
\setlength{\parskip}{0pt}
\item Define a forecast-to-plan feasibility layer separating diagnostic accuracy from operational utility.
\item Quantify the planning-execution gap using execution violation rate and normalized planning loss.
\item Compare six strategy families under the same feasibility evaluation across data-informed execution-risk scenarios.
\item Validate, across Favorita, M5, and secondary Walmart evidence, that strategy rankings shift with scenario, hierarchy, and context.
\item Translate the findings into a decision-layer framework for feasibility-aware strategy selection.
\end{itemize}

The remaining sections follow the same arc as the four symptoms in Section~\ref{sec:gap}: Section~\ref{sec:methods} defines the decision layer, Section~\ref{sec:results} reports how often and why accuracy-first and operational-loss-best selection diverge, Section~\ref{sec:strategy-constraints} organizes the evidence into strategy-selection guidance, and Section~\ref{sec:validation} checks whether the findings remain visible under tighter execution risk, coarser and finer planning grains, and a second dataset with a different cadence and business context.
