\section{Data Collection and Experimental Design}

The empirical design uses DataCo, Favorita, M5, and Walmart for distinct operational roles. Table~\ref{tab:dataset-roles} summarizes these roles. DataCo is not treated as an inventory-control dataset; it transfers empirical heterogeneity in execution risk into scenario design. Favorita is the main forecast-to-plan proof-of-concept dataset. M5 tests hierarchy and intermittent-demand robustness. Walmart is included as verified secondary business-context robustness.

\input{tables/dataset_roles_table}

\textbf{DataCo execution-risk anchor.} DataCo contains supply-chain fulfillment records with late-delivery outcomes. The analysis extracts late-delivery anchors from context-level percentiles. The current generated anchors range from 0.535 at the low-risk percentile to 0.901 at the severe-risk percentile. Under the additive clipped scenario mapping, these anchors produce execution weights from 0.318 to 0.500. These are sensitivity weights, not exact dollar costs for Favorita, M5, or Walmart.

\textbf{Favorita proof of concept.} Favorita is a daily retail demand-planning panel from Corporacion Favorita. The pipeline treats each store-family pair as a planning unit and uses promotion, holiday, oil-price, transaction, and store-context information where available at planning time. Candidate forecasts include transparent baselines and machine-learning candidates such as LightGBM and XGBoost when dependencies are available (Ke et al. 2017; Chen and Guestrin 2016). The purpose is to test whether forecast-to-plan conversion changes deployable strategy ranking.

\textbf{M5 robustness design.} M5 contains 3,049 items across 10 stores, and the pipeline samples item-store series for quick and medium robustness runs (Makridakis et al. 2022). The IEOM submission uses M5 to evaluate item-store, department-store, and category-store planning grains and to test intermittent-demand buckets. This design checks whether the planning-execution gap persists when demand is sparse or aggregated.

\textbf{Walmart business-context robustness design.} Walmart provides weekly store-department sales with holiday, markdown, store, and economic context fields. The IEOM submission uses the generated Walmart outputs to compare history-only and history-plus-context candidate forecasts, holiday and markdown stress windows, weekly cadence constraints, and switch-budget sensitivity. This design checks whether the feasibility layer remains informative when the planning problem is weekly and context driven rather than daily and store-family driven.

Rossmann is not treated as a completed experiment in this IEOM draft. It remains an optional future robustness panel.
