\section*{References}

\begingroup
\setlength{\parskip}{1pt plus 1pt minus 1pt}

\hangindent=0.25in Ansari, A. F., Stella, L., Turkmen, C., Zhang, X., Mercado, P., Shen, H., Shchur, O., Rangapuram, S. S., Pineda Arango, S., Kapoor, S., Zschiegner, J., Maddix, D. C., Wang, H., Mahoney, M. W., Torkkola, K., Wilson, A. G., Bohlke-Schneider, M. and Wang, Y., Chronos: Learning the language of time series, \textit{Transactions on Machine Learning Research}, October 2024.

\hangindent=0.25in Axsater, S., \textit{Inventory Control}, 3rd Edition, Springer, 2015.

\hangindent=0.25in Bates, J. M. and Granger, C. W. J., The combination of forecasts, \textit{Operational Research Quarterly}, vol. 20, no. 4, pp. 451-468, 1969.

\hangindent=0.25in Chen, T. and Guestrin, C., XGBoost: A scalable tree boosting system, \textit{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, pp. 785-794, 2016.

\hangindent=0.25in Culot, G., Podrecca, M. and Nassimbeni, G., Artificial intelligence in supply chain management: A systematic literature review of empirical studies and research directions, \textit{Computers in Industry}, vol. 162, article 104132, 2024.

\hangindent=0.25in Das, A., Kong, W., Sen, R. and Zhou, Y., A decoder-only foundation model for time-series forecasting, \textit{Proceedings of the 41st International Conference on Machine Learning}, PMLR, vol. 235, pp. 10148-10167, 2024.

\hangindent=0.25in Elmachtoub, A. N. and Grigas, P., Smart predict, then optimize, \textit{Management Science}, vol. 68, no. 1, pp. 9-26, 2022.

\hangindent=0.25in Forrester, J. W., \textit{Industrial Dynamics}, MIT Press, Cambridge, MA, 1961.

\hangindent=0.25in Hyndman, R. J. and Koehler, A. B., Another look at measures of forecast accuracy, \textit{International Journal of Forecasting}, vol. 22, no. 4, pp. 679-688, 2006.

\hangindent=0.25in Jia, M., Schrotenboer, A. H. and Chen, F., Scenario predict-then-optimize for data-driven online inventory routing, \textit{Transportation Science}, vol. 59, no. 5, pp. 1032-1056, 2025.

\hangindent=0.25in Ke, G., Meng, Q., Finley, T., Wang, T., Chen, W., Ma, W., Ye, Q. and Liu, T., LightGBM: A highly efficient gradient boosting decision tree, \textit{Advances in Neural Information Processing Systems}, vol. 30, pp. 3146-3154, 2017.

\hangindent=0.25in Makridakis, S., Spiliotis, E. and Assimakopoulos, V., M5 accuracy competition: Results, findings, and conclusions, \textit{International Journal of Forecasting}, vol. 38, no. 4, pp. 1346-1364, 2022.

\hangindent=0.25in Mandi, J., Kotary, J., Berden, S., Mulamba, M., Bucarey, V., Guns, T. and Fioretto, F., Decision-focused learning: Foundations, state of the art, benchmark and future opportunities, \textit{Journal of Artificial Intelligence Research}, vol. 80, pp. 1623-1701, 2024.

\hangindent=0.25in Sethi, S. P. and Sorger, G., A theory of rolling horizon decision making, \textit{Annals of Operations Research}, vol. 29, no. 1-4, pp. 387-416, 1991.

\hangindent=0.25in Silver, E. A., Pyke, D. F. and Peterson, R., \textit{Inventory Management and Production Planning and Scheduling}, 3rd Edition, John Wiley and Sons, New York, 1998.

\hangindent=0.25in Stadtler, H., Kilger, C. and Meyr, H., \textit{Supply Chain Management and Advanced Planning: Concepts, Models, Software, and Case Studies}, 5th Edition, Springer, 2015.

\hangindent=0.25in Vlachos, I. and Reddy, P. G., Machine learning in supply chain management: Systematic literature review and future research agenda, \textit{International Journal of Production Research}, vol. 63, no. 16, pp. 5987-6016, 2025.

\hangindent=0.25in Walter, A., Ahsan, K. and Rahman, S., Application of artificial intelligence in demand planning for supply chains: A systematic literature review, \textit{The International Journal of Logistics Management}, vol. 36, no. 3, pp. 672-719, 2025.

\endgroup
